---
title: "Project 2 Midterm Solutions (Updated)"
author: "530395795"
format:
  html:
    code-fold: true
    embed-resources: true
---
 
## Question 1: Variance of Z

```{r}
var_X <- 0.2
var_Y <- 0.5
var_Z <- 5^2 * var_X + (-2)^2 * var_Y
var_Z
```

**Answer**: $\text{Var}(Z) = 25 \cdot 0.2 - 4 \cdot 0.5 = \boxed{7}$

------------------------------------------------------------------------

## Question 2: Binomial Distribution (n=20, p=0.7)

```{r}
n <- 20
p <- 0.7

# (1) P(X > 16)
p_more_than_16 <- 1 - pbinom(16, size=n, prob=p)
p_more_than_16

# (2) Expected Value
expected <- n * p

# (3) Standard Deviation
std_dev <- sqrt(n * p * (1 - p))
expected
std_dev
```

**Answers**: - (1) $P(X > 16) \approx \boxed{0.1071}$ - (2) Expected: $\boxed{14}$ - (3) SD: $\boxed{2.049}$

------------------------------------------------------------------------

## Question 3: No Sales Day (Binomial, n=8, p=0.1)

```{r}
p_no_sale <- dbinom(0, size=8, prob=0.1)
p_no_sale * 100
```

**Answer**: $\boxed{43.05\%}$ chance of making no sales.

------------------------------------------------------------------------

## Question 4: Standard Normal Range \[-A, A\]

```{r}
A <- qnorm(0.5 + 0.754 / 2)
A
```

**Answer**: $A \approx \boxed{1.160}$

------------------------------------------------------------------------

## Question 5: Spending at McDonald's (Normal Distribution)

```{r}
mu <- 16.40
sigma <- 2.75

# (1) P(X < 10)
p_less_than_10 <- pnorm(10, mean=mu, sd=sigma)

# (2) 10% cutoff
q_10_percent <- qnorm(0.10, mean=mu, sd=sigma)
p_less_than_10
q_10_percent
```

**Answers**: - (1) $P(X < 10) \approx \boxed{0.00997}$ - (2) 10% cutoff: $\boxed{12.88}$ dollars

------------------------------------------------------------------------

## Question 6: Interquartile Range of SAT Scores

```{r}
mu <- 1200
sigma <- 150
z_val <- qnorm(0.75)
c <- z_val * sigma
c
```

**Answer**: $c \approx \boxed{101.17}$, so IQR = $[1098.8, 1301.2]$

------------------------------------------------------------------------

## Question 7: True or False

**Answers**: a. False — t(60) variance ≈ standard normal

b.  True — $P(U < 42) \geq 0.90$ for $U \sim \chi^2(30)$

c.  False — F-distribution allows numerator df \> denominator df

d.  True — $\chi^2$ values $\geq 0$

------------------------------------------------------------------------

## Question 8: Sample Size Effects

**Answer**: (c) variance of the sample mean **decreases**

------------------------------------------------------------------------

## Question 9: Required Sample Size for Desired SE

```{r}
pop_sd <- 20.3
target_se <- 2.9
n <- (pop_sd / target_se)^2
n
```

**Answer**: $n \approx \boxed{49}$

------------------------------------------------------------------------

## Question 10: Mean and Variance of Sample Proportion

```{r}
p <- 0.55
n <- 2000

mean_phat <- p
var_phat <- p * (1 - p) / n
mean_phat
var_phat
```

**Answers**: - Mean = $\boxed{0.55}$ - Variance $= \boxed{0.00012375}$
